### 2013-03-28 doc/sosp13/tasks.tex
pagerank

Since \Grappa keeps a very large number of active workers, their context data
will not fit in cache. Therefore, the scheduler has to perform very careful
prefetching in order to reduce context switch cost to a minimum. We determined
empirically that prefetching the fourth worker in the scheduling order is
sufficient. We also prefetch three cache lines from the stack for each worker.
This makes context switching effectively free of cache misses even to hundreds
of thousands of threads. We provide an analysis of our context switch
performance in Section~\ref{eval:basic}.

>>>>

Since \Grappa keeps a very large number of active workers, their context data
will not fit in cache. By oversubscribing on the number of workers
beyond what is required for latency tolerance, the scheduler can
ensure there is always some number of context pointers in the ready
queue. This allows the scheduler to prefetch contexts into
cache. The reason this works is because the size of the L1 cache is
sufficient to hold enough contexts to tolerate the latency to main
memory. Empirically we find that prefetching the fourth worker in the scheduling order is
sufficient. This prefetching makes context switching effectively free of cache misses even to hundreds
of thousands of threads. We provide an analysis of our context switch
performance in Section~\ref{eval:basic}.
